\documentclass[letterpaper,11pt]{article}

\usepackage{lmodern}           % Cleaner font rendering
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}         % Improved text spacing/kerning
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rahul Raj} \\ \vspace{5pt}
    \small
    +91-9155881234 $|$
    \href{mailto:rahulraj94391@gmail.com}{\underline{rahulraj94391@gmail.com}} $|$
    \href{https://www.linkedin.com/in/rahulraj94391}{\underline{LinkedIn}} $|$
    \href{https://github.com/rahulraj94391}{\underline{GitHub}} $|$
    \href{https://leetcode.com/u/rahulraj94391/}{\underline{LeetCode}}
\end{center}

\vspace{-4pt}

%-----------SUMMARY-----------
\section{Summary}
\small{Android Developer with 3 years of experience building scalable, production-grade applications using Kotlin and Java. Currently at Zoho Corporation, shipping high-impact features for 100K+ users. Strong expertise in MVVM, Clean Architecture, performance optimisation, and REST API integrations.}

\vspace{2pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Zoho Corporation}{Jul 2023 -- Present}
      {Software Development Engineer}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Engineered a unified social media integration (Instagram, Twitter, Facebook) within Zoho Desk, consolidating customer support channels and reducing agent context-switching.}
        \resumeItem{Built a real-time dynamic field computation engine that evaluates dependent field values via live API calls and local DB sync, eliminating manual data re-entry and ensuring consistency across specific field types.}
        \resumeItem{Refactored existing layouts and custom views to support RTL rendering in Zoho Desk, expanding the app's reach to Arabic and Hebrew-speaking markets.}
        \resumeItem{Achieved WCAG compliance and integrated TalkBack support across key user flows, making Zoho Desk accessible to users with visual and motor disabilities in line with Google's accessibility standards.}
        \resumeItem{Developed and maintained features for an internal reusable Android component library powering dynamic, user-configurable field display layouts --- including drag-and-drop reordering, multi-layout support, and advanced styling options --- shipped across multiple Zoho mobile applications.}
      \resumeItemListEnd

    \resumeSubheading
      {Zoho Corporation}{Apr -- Jun 2022}
      {Summer Intern}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Developed a Ticket Booking System console application using Java and Kotlin.}
        \resumeItem{Implemented algorithms for seat allocation and train scheduling.}
        \resumeItem{Applied OOP and SOLID principles for modular, maintainable code structure.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{SociableX} $|$ \emph{Kotlin, Java, MVVM, Clean Architecture, Coroutines, Room, Hilt} $|$ \href{https://github.com/rahulraj94391/SociableX}{\underline{GitHub}}}{}
        \resumeItemListStart
          \resumeItem{Developed a feature-rich social media Android app with search, hashtag and location-based photo viewing, profile sharing, real-time messaging, and biometric app locking.}
          \resumeItem{Used Coroutine Worker for background task scheduling; followed MVVM and Clean Architecture for scalable, testable code.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{E-Commerce Web Application} $|$ \emph{Spring Boot, Spring Security, JPA, Hibernate, JWT, AWS}}{}
        \resumeItemListStart
          \resumeItem{Built a complete eCommerce backend with modules for Product, Category, Authentication, Cart, Order Management, and Payment.}
          \resumeItem{Implemented JWT-based authentication with role and permission management for fine-grained access control.}
          \resumeItem{Integrated pagination and sorting for scalable product and order listings; used Lombok to reduce boilerplate.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Kotlin, Java} \\[3pt]
      \textbf{Android}{: Android SDK, Jetpack (ViewModel, LiveData, Room, Navigation, WorkManager), Retrofit, Coroutines, Hilt/Dagger} \\[3pt]
      \textbf{Architecture}{: MVVM, Clean Architecture, Repository Pattern} \\[3pt]
      \textbf{Tools \& Platforms}{: Android Studio, Git, Firebase, REST APIs, Postman, AWS} \\[3pt]
      \textbf{Other}{: Spring Boot, JPA, Hibernate, JWT, SQL}
    }}
  \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vel Tech University}{2019 -- 2023}
      {Bachelor of Technology, Computer Science and Engineering \normalfont{$|$ CGPA: 8.6/10}}{Chennai, India}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \item
    \resumeItemListStart
      \resumeItem{Solved \textbf{350+} coding problems on LeetCode, GeeksforGeeks, and Code360.}
      \resumeItem{Mentored students in Java and Data Structures \& Algorithms (DSA) as part of a college programming club.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}